TBD

### 2020-10-05 Articles/2020-ClassicalMechanicsPhil/Source/classical-phil-article.tex
Update classical-phil-article.tex
Added notes for response to Curiel
Adding note on strong/weak assumption

@@

@@

@@

@@

>>>>

\usepackage{amsmath}

@@

%% testing from desktop

@@

\subsubsection{Strong vs weak Kinematic assumption}

Problem: changing variables from state variables $(q^i, p_j)$ to kinematic variables $(x^i, v^j)$. We set $x^i=q^i$. The change of name helps us remember that $\frac{\partial}{\partial x^i} \neq \frac{\partial}{\partial q^i}$ as one is taken at constant $v$ while the other is taken at constant $p$.

Weak assumptions: $v^i = v^i(q^j, p^k)$ invertible. Strong assumptions: $m v^i = g^{ij} (p_j - q A_j(q^k))$ linear in $p_j$.

We want to transport the density from state variables to initial conditions: $\rho(q^i, p_j) = |J| \rho(x^i, v^j)$. We have:
\begin{equation}
	|J| = \begin{bmatrix}
	\frac{\partial x^i}{\partial q^j} & \frac{\partial v^i}{\partial q^j} \\
	\frac{\partial x^i}{\partial p_j} & \frac{\partial v^i}{\partial p_j}
	\end{bmatrix}
	= \begin{bmatrix}
	\delta^i_j & \frac{\partial v^i}{\partial q^j} \\
	0 & \frac{\partial v^i}{\partial p_j}
	\end{bmatrix}
	= \left|\frac{\partial v^i}{\partial p_j}\right|
\end{equation}
Under the strong assumption, $\left|\frac{\partial v^i}{\partial p_j}\right| = \frac{1}{m} |g^{ij}|$.

@@

Response: symplectic geometry indeed does not care about the difference between q's and p's. Classical mechanics does. Misindentification of the math (symplectic geometry) with the physics (Classical Hamiltonian mechanics).

@@

%
